Damage localization based on vibrations

### 2016-12-07 slides/slides.tex
slides xtra

  \title{Damage localization based on vibrations}
  \author{Benjamin Fasquelle, Nicolas Pompidor and Jimmy Rogala}
  \institute{École Normale Supérieure de Rennes, département Informatique et Télécommunications}

@@

%\AtBeginSection[]
%{
%  \begin{frame}<beamer>
%    \frametitle{Sommaire}
%{\scriptsize\tableofcontents[currentsection]
%}
%  \end{frame}
%}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\subsection{Purpose}
\begin{frame}{Purpose}

@@

\begin{center}
\begin{itemize}
\item<1-> Detection: Is the structure damaged or not?
\vspace{1\baselineskip}
\item<2-|alert@5> Localization: Where is the damaged area located?
\vspace{1\baselineskip}
\item<3-> Quantification: What is the extent of damage?
\vspace{1\baselineskip}
\item<4-> Prediction: What is the remaining service life of the structure?
\end{itemize}
\end{center}
\end{frame}

@@

\setbeamertemplate{itemize item}{\color{green}$\checkmark$}
\begin{columns}
		\begin{column}{0.5\textwidth} 
		\begin{center}
			\begin{itemize}
				\item Detailed information about a local damage state
			\end{itemize}
		\end{center}
		\end{column}
		\begin{column}{0.5\textwidth}
		\begin{center}
		\setbeamertemplate{itemize item}{\color{red}$\times$}
			\begin{itemize}
				\item Requires to know area where it is located
				\item May be costly
				\item Taking a long time to be performed
				\item Hope for easy access
			\end{itemize}
		\end{center}
		\end{column}
	\end{columns}
	\pause
	\begin{center}
	\textcolor{red}{{\large 
$\Rightarrow$ Global methods automated and based on sensor measurements were developed.}}

@@

\vspace{1\baselineskip}
\item Modal characteristics is the experimental data used for damage
assessment through FE model updating.
\vspace{1\baselineskip}
\item Different types of modal data can be used (natural frequencies, eigenvalues, etc).
\end{itemize}
\end{center}
\end{frame}

@@

@@

\begin{center}
Data driven method
\end{center}

\underline{Main steps}:
\begin{itemize}
\item Frequency Response Function (FRF) calcul
\item Interpolation on the FRF
\item Error calcul
\end{itemize}

\subsection{FRF calcul}
\begin{frame}{FRF calcul}
\begin{exampleblock}{Frequency Response Function}
\begin{center}
$H = \frac{Y}{F}$
\end{center}
$F$: input

\subsection{Error calcul}
\begin{frame}{Error calcul}

\section{Physical Models}

\subsection{Finite Elements model}
\begin{frame}{Finite Elements model}

@@

@@

@@

FRF for one sensor against frequencies
\end{center}
\end{frame}

@@

\underline{What we will do:}
\begin{itemize}
\item Development of a statistical extension of this method
\end{itemize}

>>>>

  \title{Damage localization based on vibrations}
  \author{Benjamin Fasquelle, Nicolas Pompidor and Jimmy Rogala}
  \date{Supervised by Michael Döhler}
  \institute{\textit{École Normale Supérieure de Rennes, département Informatique et Télécommunications}}

@@

\AtBeginSection[]
{
  \begin{frame}<beamer>
  \setcounter{tocdepth}{1}
{\tableofcontents[currentsection]
}
  \end{frame}
}

@@

\begin{frame}<beamer>
  \setcounter{tocdepth}{1}
{\tableofcontents
}
\end{frame}

\section{Introduction}

\subsection{Purpose}

\begin{frame}{Purpose}

@@

\begin{center}
\begin{itemize}
\item<1-> {\only<5-6>{\color{green}}Detection: Is the structure damaged or not?}
\vspace{1\baselineskip}
\item<2-|alert@6> Localization: Where is the damaged area located?
\vspace{1\baselineskip}
\item<3-> Quantification: What is the extent of damage?
\vspace{1\baselineskip}
\item<4-> Prediction: What is the remaining service life of the structure?
\end{itemize}
\end{center}
\end{frame}

@@

\setbeamertemplate{itemize item}{\color{green}$\checkmark$}
\begin{columns}
		\begin{column}{0.5\textwidth} 
		\begin{center}
			\begin{itemize}
				\item Detailed information about a local damage state
			\end{itemize}
		\end{center}
		\end{column}
		\begin{column}{0.5\textwidth}
		\begin{center}
		\setbeamertemplate{itemize item}{\color{red}$\times$}
			\begin{itemize}
				\item Require to know area where it is located
				\item May be costly
				\item Taking a long time to be performed
				\item Hope for easy access
			\end{itemize}
		\end{center}
		\end{column}
	\end{columns}
	\pause
	\begin{center}
	\textcolor{red}{{\large 
$\Rightarrow$ Global methods automated and based on sensor measurements were developed.}}

@@

\vspace{1\baselineskip}
\item Modal characteristics is the experimental data used for damage
assessment through FE model updating.
\vspace{1\baselineskip}
\item Different types of modal data can be used (natural frequencies, eigenvalues, etc).
\end{itemize}
\end{center}

\begin{block}{}
Applicable to arbitrary structural types, but a precise model is required
\end{block}

@@

\begin{block}{}
Require no complicated model, allowing a simple and fast evaluation, but usually many sensors are required
\end{block}

@@

\section{Vibration modelling}

\subsection{Vibration modelling}
\begin{frame}{Vibration modelling}

@@

\begin{center}
\textbf{Data driven method}

\textit{Damage localization in bridges via the FRF interpolation method}, by M. Dilena, M.P. Limongelli, A. Morassi
\end{center}

\underline{Main steps}:
\begin{itemize}
\item Frequency Response Function (FRF) computation
\item Interpolation on the FRF
\item Error computation
\end{itemize}

\subsection{FRF computation}
\begin{frame}{FRF computation}
\begin{exampleblock}{Frequency Response Function}
\begin{center}
$H = \frac{Y}{F}$
\end{center}
$F$: input

\subsection{Error computation}
\begin{frame}{Error computation}

@@

\begin{frame}{System masses-springs}

\begin{exampleblock}{Stiffness}
\begin{center}
$
K = 
\begin{pmatrix} 
k_1 + k_2 & - k_1 \\ 
- k_1 &\ddots\\ 
& -k_i & k_i + k_{i+1} & -k_{i+1} \\
&&&\ddots& -k_n\\
&&& -k_n & k_n
\end{pmatrix}
$
\end{center}
\end{exampleblock}

\begin{exampleblock}{Damping: Rayleigh case}
\begin{center}
$C = \alpha M + \beta K,\ \ \ \ \ \alpha, \beta \in \mathbb{R}_+$
\end{center}
\end{exampleblock}

@@

FRF for one sensor against frequencies
\end{center}

Natural frequencies (Hz):
0.04,
0.14,
0.23,
0.31,
0.39,
0.46,
0.52,
0.57,
0.60,
0.62

@@

\underline{What we will do:}
\begin{itemize}
\item More detailed evaluation
\item Development of a statistical extension of this method
\end{itemize}
